Optimal Estimation with Nuisance Parameters

### 2024-03-06 src/explore/20240216-optest.qmd
I showed that the conditional expectation is the optimal function.

  big_v <- matrix(0, nrow = 8, ncol = 8)
  big_v[1:4, 1:4] <- 
    diag(c(1 / df$pi_11[1] * Ex12 - Ex1^2,
           1 / df$pi_10[1] * Ex12 - Ex1^2,
           1 / df$pi_01[1] * Ex12 - Ex1^2,
           1 / df$pi_00[1] * Ex12 - Ex1^2))
  big_v[5:6, 5:6] <- 
  diag(c(1 / df$pi_11[1] * Ex22 - Ex2^2,
         1 / df$pi_10[1] * Ex22 - Ex2^2))
  big_v[7:8, 7:8] <- 
    diag(c(1 / df$pi_11[1] * Ey2 - Ey^2,
           1 / df$pi_01[1] * Ey2 - Ey^2))

  big_v[1, 5] <- 1 / df$pi_11[1] * Ex1x2 - Ex1 * Ex2
  big_v[1, 7] <- 1 / df$pi_11[1] * Ex1y - Ex1 * Ey
  big_v[5, 7] <- 1 / df$pi_11[1] * Ex2y - Ex2 * Ey
  big_v[2, 6] <- 1 / df$pi_10[1] * Ex1x2 - Ex1 * Ex2
  big_v[3, 8] <- 1 / df$pi_01[1] *  Ex1y - Ex1 * Ey

@@

$$
\Var(\hat f_1^{(11)}) = n^{-1}(\pi_{11}^{-1} E[X_1^2] - E[X_1]^2).
$$

@@

$$
\Cov(\hat f_1^{(11)}, \hat f_2^{(11)}) =
n^{-1}(\pi_{11}^{-1} E[X_1 X_2] - E[X_1]E[X_2]).
$$

>>>>

  big_v <- matrix(0, nrow = 8, ncol = 8)
  big_v[1:4, 1:4] <- 
    diag(c(1 / df$pi_11[1] * (Ex12 - Ex1^2),
           1 / df$pi_10[1] * (Ex12 - Ex1^2),
           1 / df$pi_01[1] * (Ex12 - Ex1^2),
           1 / df$pi_00[1] * (Ex12 - Ex1^2)))
  big_v[5:6, 5:6] <- 
  diag(c(1 / df$pi_11[1] * (Ex22 - Ex2^2),
         1 / df$pi_10[1] * (Ex22 - Ex2^2)))
  big_v[7:8, 7:8] <- 
    diag(c(1 / df$pi_11[1] * (Ey2 - Ey^2),
           1 / df$pi_01[1] * (Ey2 - Ey^2)))

  big_v[1, 5] <- 1 / df$pi_11[1] * (Ex1x2 - Ex1 * Ex2)
  big_v[1, 7] <- 1 / df$pi_11[1] * (Ex1y - Ex1 * Ey)
  big_v[5, 7] <- 1 / df$pi_11[1] * (Ex2y - Ex2 * Ey)
  big_v[2, 6] <- 1 / df$pi_10[1] * (Ex1x2 - Ex1 * Ex2)
  big_v[3, 8] <- 1 / df$pi_01[1] *  (Ex1y - Ex1 * Ey)

@@

$$
\Var(\hat f_1^{(11)}) = n^{-1}\pi_{11}^{-1} (E[X_1^2] - E[X_1]^2).
$$

@@

$$
\Cov(\hat f_1^{(11)}, \hat f_2^{(11)}) =
n^{-1}\pi_{11}^{-1} (E[X_1 X_2] - E[X_1]E[X_2]).
$$
